### 2025-07-12 multiple-regression.qmd
20250712 - BCa confidence interval

# Function for fitting the models on the bootstrap samples
fit_lm <- function(split) {
  analysis_data <- rsample::analysis(split)
  fit <- workflows::fit(lm_workflow, data = analysis_data)
  broom::tidy(fit)
}

@@

# Extract bootstrapped coefficients
boot_coefs <- 
  boot_models %>% 
  tidyr::unnest(coef_info)

# Compute percentile intervals for the regression coefficients
percentile_intervals <- rsample::int_pctl(boot_models, coef_info)

percentile_intervals
```

>>>>

# Function for fitting the models on the bootstrap samples
fit_lm <- function(split, ...) {
  analysis_data <- rsample::analysis(split)
  fit <- workflows::fit(lm_workflow, data = analysis_data)
  broom::tidy(fit)
}

@@

# Extract bootstrapped coefficient estimates
boot_coefs <- boot_models %>%
  tidyr::unnest(coef_info)

# Percentile confidence intervals
percentile_intervals <- rsample::int_pctl(
  .data = boot_models,
  statistics = coef_info)

# Bias-corrected and accelerated confidence intervals
bca_intervals <- rsample::int_bca(
  .data = boot_models,
  statistics = coef_info,
  .fn = fit_lm
)

# View confidence intervals
percentile_intervals
bca_intervals
```
